---
title: "Juan Midterm"
author: "Diwei Zhu"
date: "2021/11/15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r import car library}
library(car)
```

### 1. Importing dataset
```{r importing data}
df <- read.csv("C:/YICHEN WANG/Course/2021 FALL/MGSC661/project/film.csv")

attach(df)
```

### 2. Examining, cleaning, and modifying the dataset
2.1) Investigate Correlation between predictors (Collinearity Problem)
```{r colinearity}
# selecting columns with numeric values
# install.packages("dplyr")
library(dplyr)
quantvars <- select_if(df, is.numeric)

# dropping IMDB score and columns include NA
quantvars <- quantvars[-c(1, 23, 26)]
quantvars
View(quantvars)

# populating correlation matrix
corr_matrix = cor(quantvars)
corr_matrix <- round(corr_matrix, 2)
#options(max.print=999999)
#write.csv(corr_matrix, "corr_matrix.csv")

# visualize correlation
install.packages("ggcorrplot")
library(ggcorrplot)
ggcorrplot(corr_matrix)
```

2.2) Dummifying language & main_production_country
```{r dummify}
#install.packages('fastDummies')
library(fastDummies)

df <- dummy_cols(df, select_columns = "main_lang")
df <- dummy_cols(df, select_columns = "main_production_country")
```


### 3. Exploring variables
3.1) histograms and boxplots of numerical variables
```{r histograms and boxplots}
hist(imdb_score)
boxplot(imdb_score, main = "boxplot of imdb_score")

hist(budget_in_millions)
boxplot(budget_in_millions, main = "boxplot of budget_in_millions")

hist(month_of_release)
boxplot(month_of_release, main = "boxplot of month_of_release")

hist(year_of_release)
boxplot(year_of_release, main = "boxplot of year_of_release")

hist(duration_in_hours)
boxplot(duration_in_hours, main = "boxplot of duration_in_hours")

hist(total_number_languages)
boxplot(total_number_languages, main = "boxplot of total_number_languages")

hist(total_number_of_actors)
boxplot(total_number_of_actors, main = "boxplot of total_number_of_actors")

hist(total_number_of_directors)
boxplot(total_number_of_directors, main = "boxplot of total_number_of_directors")

hist(total_number_of_producers)
boxplot(total_number_of_producers, main = "boxplot of total_number_of_producers")

hist(total_number_of_production_companies)
boxplot(total_number_of_production_companies, main = "boxplot of total_number_of_production_companies")

hist(total_number_of_production_countries)
boxplot(total_number_of_production_countries, main = "boxplot of total_number_of_production_countries")
```


### 4. Feature selection
4.1) Step1 - to find the benchmark R-squared - building model including all numeric predictors
```{r benchmark}
library(dplyr)
attach(df)

# Step1 - to find the benchmark R-squared - building model including all numeric predictors
quantvars <- select_if(df, is.numeric) # Select only numeric variables from dataframe
predictors_i <- colnames(quantvars)[2 : ncol(quantvars)]    # Create vector of predictor names
benchmark.r <- summary(lm(imdb_score ~ ., quantvars[ , c("imdb_score", predictors_i)]))$adj.r.squared
benchmark.r
```

4.2) Step2 - dropping predictors one by one  
```{r drop predictors}
predictor <- c() # create vector to store predictor's name to be removed
rsq <- c() # create vector to store r-squared without certain predictor

for(i in 2:ncol(quantvars)) {                 # Head of for-loop
  quantvars <- select_if(df, is.numeric)      # import numeric dataframe
  predictor <- append(predictor, colnames(quantvars[c(i)]))   # indexing removed predictor
  quantvars <- quantvars[-c(i)]               # drop one predictor per iteration
  predictors_i <- colnames(quantvars)[2:ncol(quantvars)]    # Create vector of predictor names
  rsq <- append(rsq, summary(                 # Store regression model's rsquared into vector
    lm(imdb_score ~ ., quantvars[,c("imdb_score", predictors_i)]))$adj.r.squared)
}
```

4.3) Step3 - interpreting the result (guage incremental r-square per each predictor)
```{r interpretation}
result.df<- data.frame(predictor, rsq)
result.df[order(result.df$rsq),] 

# top 10 predictors are most meaningul features to increase R-squared of lr model
meaningful.predictors <- result.df[order(result.df$rsq),][c(1:10),1] 
```

4.4) Step4 - populating new data tables with meaningful features (+ budget)
```{r new table}
# dataframe only including predictors found from r-squared approach
new_df <- quantvars[, c("imdb_score", meaningful.predictors)] 
write.csv(quantvars[, c("imdb_score", meaningful.predictors)], 'new_df.csv')

# dataframe also including predictors found from random forest
new_df_randomforest <- quantvars[, c("imdb_score", "budget_in_millions", "genre_drama", meaningful.predictors)] 
```

4.5) Visualizing and re-exploring the 12 selected predictors
```{r visualize selected predictors}
attach(new_df_randomforest)
par(mfrow=c(3,4))
plot(year_of_release,imdb_score)
plot(duration_in_hours,imdb_score)
plot(genre_horror,imdb_score)
plot(genre_action,imdb_score)
plot(genre_comedy,imdb_score)
plot(genre_animation,imdb_score)
plot(genre_family,imdb_score)
plot(genre_history,imdb_score)
plot(main_actor1_is_female,imdb_score)
plot(total_number_of_actors,imdb_score)
plot(budget_in_millions,imdb_score)
plot(genre_drama,imdb_score)
```



4.6) residual plot for checking non-linearity
You need to hit enter for two times in the console to load the images.
```{r residual plot}
require(caTools)
x = lm(imdb_score~budget_in_millions+year_of_release +duration_in_hours+total_number_of_actors+genre_action+genre_animation+genre_comedy+genre_drama+ genre_family+genre_history+genre_horror+main_actor1_is_female)
residualPlots(x)
```


### 5. Cleaning outliers
5.1) Based on selected features above , let see if there is any observations/outliners we could observe and remove amoung predictors
```{r find outliers}


attach(new_df_randomforest)
reg_year_release =lm(imdb_score~year_of_release)
summary(reg_year_release)
outlierTest(reg_year_release)
##observations:633,895,2310,2718,2045,526

reg_duration =lm(imdb_score~duration_in_hours)
summary(reg_duration)
outlierTest(reg_duration)
##observations:633,895

reg_genre_horror=lm(imdb_score~genre_horror)
summary(reg_genre_horror)
outlierTest(reg_genre_horror)
##observations:633,895,575,2045

reg_genre_action =lm(imdb_score~genre_action)
summary(reg_genre_action)
outlierTest(reg_genre_action)
##observations:633,895

reg_genre_comdedy= lm(imdb_score~genre_comedy)
summary(reg_genre_comdedy)
outlierTest(reg_genre_comdedy)
##observations:633,895,2045

reg_genre_animation =lm(imdb_score~genre_animation)
summary(reg_genre_animation)
outlierTest(reg_genre_animation)
##observations:633,895

reg_genre_family=lm(imdb_score~genre_family)
summary(reg_genre_family)
outlierTest(reg_genre_family)
##observations:633,895

reg_genre_history=lm(imdb_score~genre_history)
summary(reg_genre_history)
outlierTest(reg_genre_history)
##observations:633,895

reg_actor1_female=lm(imdb_score~main_actor1_is_female)
summary(reg_actor1_female)
outlierTest(reg_actor1_female)
##observations:633,895

reg_total_actors=lm(imdb_score~total_number_of_actors)
summary(reg_total_actors)
outlierTest(reg_total_actors)
##observations:633,895,2045

reg_budget=lm(imdb_score~budget_in_millions)
summary(reg_budget)
outlierTest(reg_budget)
##observations:633,895

reg_genre_drama= lm(imdb_score~genre_drama)
summary(reg_genre_drama)
outlierTest(reg_genre_drama)
##observations:633,895
```

5.2) remove outliers
```{r remove outliers}
## From all above, we could remove observation number: 575,633,895,2310,2718,2045,526
## remove them from the "new_df" dataset

new_df_randomforest = new_df_randomforest[-c(575,633,895,2310,2718,2045,526),]
```


### 6. Adding polynomial
6.1) year_of_release
```{r polynomial_year of release}
#year of release
reg1 = lm(imdb_score~poly(year_of_release,1)+poly(duration_in_hours,1)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg2 = lm(imdb_score~poly(year_of_release,2)+poly(duration_in_hours,1)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg3 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,1)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg4 = lm(imdb_score~poly(year_of_release,4)+poly(duration_in_hours,1)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
print(anova(reg1,reg2,reg3,reg4))
#for year_of_release, degree of 3 is chosen because from degree 3 to 4, Pr(>f) increases
#significantly, but the RSS does not reduce much.
```

6.2) duration_in_hours
```{r polynomial_duration_in_hours}
#duration_in_hours
reg5 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,1)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg6 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,2)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg7 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,3)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg8 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg9 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,5)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
print(anova(reg5,reg6,reg7,reg8,reg9))
#for year_of_release, degree of 4 is chosen because from degree 4 to 5, Pr(>f) increases
#significantly, but the RSS does not reduce much.
```

6.3) total_number_of_actors
```{r polynomial_total_number_of_actors}
#total_number_of_actors
reg10 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,1)+poly(budget_in_millions,1))
reg11 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,1))
reg12 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,3)+poly(budget_in_millions,1))
reg13 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,4)+poly(budget_in_millions,1))
print(anova(reg10,reg11,reg12,reg13))
#for year_of_release, degree of 2 is chosen because from degree 2 to 3, Pr(>f) increases
#significantly, but the RSS does not reduce much.
```

6.4) budget_in_millions
```{r polynomial_budget_in_millions}
#budget_in_millions
reg14 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,1))
reg15 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,2))
reg16 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,3))
reg17 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,4))
reg18 = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,5))
print(anova(reg14,reg15,reg16,reg17,reg18))
#for year_of_release, degree of 4 is chosen because from degree 4 to 5, Pr(>f) increases
#significantly, but the RSS does not reduce much.
```

6.5) polynomial result
```{r polynomial result}
final_reg = lm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)
            +poly(total_number_of_actors,2)+poly(budget_in_millions,4)
            +genre_horror+genre_action+genre_comedy+genre_animation
            +genre_family+genre_history+main_actor1_is_female)
#final degree: year_of_release=3, duration_in_hours=4, total_number_of_actors=2 and budget_in_millions=4
summary(final_reg)
```
The polynomial model improved r^2 from 0.3174 to 0.3631


### 7. Detecting splines and build spline model
```{r splines}
library(splines)
library(boot)
attach(new_df_randomforest)

#1) Testing linear splines
#define function to give knot locations for any number of splines and a given column name
get_knots <- function(num_splines, column_name){
  spline_increment = 1/num_splines
  spline_percentile = 0
  knots = c()
  for (j in seq(num_splines - 1)){
    spline_percentile = spline_percentile + spline_increment
    knot = quantile(column_name, spline_percentile)
    knots = c(knots,knot)
  }
  return(knots)
}


#Test number of splines
min_mse = 10000000
for (i in seq(2,5)) {
  fit=glm(imdb_score ~ bs(year_of_release, knots = get_knots(i, new_df_randomforest$year_of_release), degree=1) +
            bs(budget_in_millions, knots = get_knots(i, new_df_randomforest$budget_in_millions), degree=1) +
            bs(genre_drama, knots = get_knots(i, new_df_randomforest$genre_drama), degree=1) +
            bs(duration_in_hours, knots = get_knots(i, new_df_randomforest$duration_in_hours), degree=1) +
            bs(genre_horror, knots = get_knots(i, new_df_randomforest$genre_horror), degree=1) +
            bs(genre_action, knots = get_knots(i, new_df_randomforest$genre_action), degree=1) +
            bs(total_number_of_actors, knots = get_knots(i, new_df_randomforest$total_number_of_actors), degree=1) +
            bs(genre_comedy, knots = get_knots(i, new_df_randomforest$genre_comedy), degree=1) +
            bs(genre_animation, knots = get_knots(i, new_df_randomforest$genre_animation), degree=1) +
            bs(genre_action, knots = get_knots(i, new_df_randomforest$genre_action), degree=1) +
            bs(genre_family, knots = get_knots(i, new_df_randomforest$genre_family), degree=1) +
            bs(main_actor1_is_female, knots = get_knots(i, new_df_randomforest$main_actor1_is_female), degree=1)
           )
  
  mse=round(cv.glm(new_df_randomforest, fit, K=10)$delta[1],3)
  
  if (mse <= min_mse){
    min_mse = mse
    best_i = i
  }
}
print(min_mse, best_i)

#We see that the optimal number of splines is 5, with 4 knots. This gives us an mse of 0.593. 
#Now we will test different polynomial degrees for the splines to see if we can improve this.

#2)Tesitng polynomial splines

library(splines)
library(boot)
attach(new_df_randomforest)


#define function to give knot locations for any number of splines and a given column name
get_knots <- function(num_splines, column_name){
  spline_increment = 1/num_splines
  spline_percentile = 0
  knots = c()
  for (j in seq(num_splines - 1)){
    spline_percentile = spline_percentile + spline_increment
    knot = quantile(column_name, spline_percentile)
    knots = c(knots,knot)
  }
  return(knots)
}


#Test number of splines
min_mse = 10000000
for (i in seq(2,5)) {
  fit=glm(imdb_score ~ bs(year_of_release, knots = get_knots(i, new_df_randomforest$year_of_release), degree=1) +
            bs(budget_in_millions, knots = get_knots(i, new_df_randomforest$budget_in_millions), degree=1) +
            bs(genre_drama, knots = get_knots(i, new_df_randomforest$genre_drama), degree=1) +
            bs(duration_in_hours, knots = get_knots(i, new_df_randomforest$duration_in_hours), degree=1) +
            bs(genre_horror, knots = get_knots(i, new_df_randomforest$genre_horror), degree=1) +
            bs(genre_action, knots = get_knots(i, new_df_randomforest$genre_action), degree=1) +
            bs(total_number_of_actors, knots = get_knots(i, new_df_randomforest$total_number_of_actors), degree=1) +
            bs(genre_comedy, knots = get_knots(i, new_df_randomforest$genre_comedy), degree=1) +
            bs(genre_animation, knots = get_knots(i, new_df_randomforest$genre_animation), degree=1) +
            bs(genre_action, knots = get_knots(i, new_df_randomforest$genre_action), degree=1) +
            bs(genre_family, knots = get_knots(i, new_df_randomforest$genre_family), degree=1) +
            bs(main_actor1_is_female, knots = get_knots(i, new_df_randomforest$main_actor1_is_female), degree=1))
}
#   print("mse for linear spline:")
#   print(round(cv.glm(new_df_randomforest, fit, K=10)$delta[1],3))
#   
#   if (mse <= min_mse){
#     min_mse = mse
#     best_i = i
#   }
# }
# print(min_mse, best_i)

#We see that the optimal number of splines is 5, with 4 knots. This gives us an mse of 0.592. 
#Now we will test different polynomial degrees for the splines to see if we can improve this.


####part for finding the optimal degree for polynomial splines####
#--------------------------------------------------------------------------------------------------
#create matrix with all options of polynomial degrees
# m <- expand.grid(2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3, 2:3)
# 
# min_mse <- 1000000
# best_a = 0
# best_b = 0
# best_c = 0
# best_d = 0
# best_e = 0
# best_f = 0
# best_g = 0
# best_h = 0
# best_i = 0
# best_j = 0
# best_k = 0
# best_l = 0
# best_m = 0
# n = 1
# 
# #loop through all options to fit and evaluate model
# for (i in seq(nrow(m))){
#   a = m[i,1]
#   b = m[i,2]
#   c = m[i,3]
#   d = m[i,4]
#   e = m[i,5]
#   f = m[i,6]
#   g = m[i,7]
#   h = m[i,8]
#   i_ = m[i,9]
#   j = m[i,10]
#   k = m[i,11]
#   l = m[i,12]
#   m_ = m[i,13]
#   
#   print(n)
#   n = n+1
#   
#   fit = glm(imdb_score ~ bs(year_of_release, knots = get_knots(5, new_df_randomforest$year_of_release), degree=a) +
#             bs(budget_in_millions, knots = get_knots(5, new_df_randomforest$budget_in_millions), degree=b) +
#             bs(genre_drama, knots = get_knots(5, new_df_randomforest$genre_drama), degree=c) +
#             bs(duration_in_hours, knots = get_knots(5, new_df_randomforest$duration_in_hours), degree=d) +
#             bs(genre_horror, knots = get_knots(5, new_df_randomforest$genre_horror), degree=e) +
#             bs(genre_action, knots = get_knots(5, new_df_randomforest$genre_action), degree=f) +
#             bs(total_number_of_actors, knots = get_knots(5, new_df_randomforest$total_number_of_actors), degree=g) +
#             bs(genre_comedy, knots = get_knots(5, new_df_randomforest$genre_comedy), degree=h) +
#             bs(genre_animation, knots = get_knots(5, new_df_randomforest$genre_animation), degree=i_) +
#             bs(genre_action, knots = get_knots(5, new_df_randomforest$genre_action), degree=j) +
#             bs(genre_family, knots = get_knots(5, new_df_randomforest$genre_family), degree=k) +
#             bs(main_actor1_is_female, knots = get_knots(5, new_df_randomforest$main_actor1_is_female), degree=l) + 
#             bs(genre_family, knots = get_knots(5, new_df_randomforest$genre_family), degree=m_))
#   
#   mse=round(cv.glm(new_df_randomforest, fit, K=5)$delta[1],3)
#   
#   if (is.nan(mse)){
#     next
#   }
#   if (mse <= min_mse){
#     min_mse = mse
#     best_a = a
#     best_b = b
#     best_c = c
#     best_d = d
#     best_e = e
#     best_f = f
#     best_g = g
#     best_h = h
#     best_i = i_
#     best_j = j
#     best_k = k
#     best_l = l
#     best_m = m_
#   }
# }
# 
# print(c(min_mse,best_a, best_b, best_c, best_d, best_e, best_f, best_g, best_h, best_i, best_j, best_k, best_l, best_m))
#-------------------------------------------------------------------------------------------------------------------
#warning: this test takes about an hour to run, which is why I only tried degrees 2 and 3
#After testing polynomial splines, we can get the mse down to 0.586, an improvement over linear splines.
#This occurs with the following polynomial degrees (ordered by how they appear in the code): 2,3,2,2,3,3,2,3,3,3,3,2,2

#printing results
labels = c('best_a', 'best_b', 'best_c', 'best_d', 'best_e', 'best_f', 'best_g', 'best_h', 'best_i', 'best_j', 'best_k', 'best_l', 'best_m')
optimal_degrees = c(2,3,2,2,3,3,2,3,3,3,2,3,2)
best_degrees = data.frame(labels, optimal_degrees)
fit1 = glm(imdb_score ~ bs(year_of_release, knots = get_knots(5, new_df_randomforest$year_of_release), degree=2) +
            bs(budget_in_millions, knots = get_knots(5, new_df_randomforest$budget_in_millions), degree=3) +
            bs(genre_drama, knots = get_knots(5, new_df_randomforest$genre_drama), degree=2) +
            bs(duration_in_hours, knots = get_knots(5, new_df_randomforest$duration_in_hours), degree=2) +
            bs(genre_horror, knots = get_knots(5, new_df_randomforest$genre_horror), degree=3) +
            bs(genre_action, knots = get_knots(5, new_df_randomforest$genre_action), degree=3) +
            bs(total_number_of_actors, knots = get_knots(5, new_df_randomforest$total_number_of_actors), degree=2) +
            bs(genre_comedy, knots = get_knots(5, new_df_randomforest$genre_comedy), degree=3) +
            bs(genre_animation, knots = get_knots(5, new_df_randomforest$genre_animation), degree=3) +
            bs(genre_action, knots = get_knots(5, new_df_randomforest$genre_action), degree=3) +
            bs(genre_family, knots = get_knots(5, new_df_randomforest$genre_family), degree=3) +
            bs(main_actor1_is_female, knots = get_knots(5, new_df_randomforest$main_actor1_is_female), degree=2))
print(round(cv.glm(new_df_randomforest, fit1, K=5)$delta[1],3))
```


### 8. Testing 
```{r testing}
#testing results
#install.packages('caTools')
library(caTools)

fit2 = glm(imdb_score~poly(year_of_release,3)+poly(duration_in_hours,4)+poly(total_number_of_actors,2)+poly(budget_in_millions,4)+genre_horror+genre_action+genre_comedy+genre_animation+genre_family+genre_history+main_actor1_is_female, data=new_df_randomforest)

print(round(cv.glm(new_df_randomforest, fit2, K=5)$delta[1],3))

```
###9. correct heteroskedaticity
```{r heteroskedaticity}
library(boot)
require(caTools)
require(methods)
require(lmtest)
require(plm)

plot(predict(final_reg),residuals(final_reg),col="red")
abline(0,0,lty=2)

# test heteroskedaticity
print("before eliminating heteroskedasticity:")
print(summary(final_reg))

# p = 3.8913e-07, smaller than 0.05. There is heteroskedasticity.
print("after eliminating heteroskedasticity:")
print(coeftest(final_reg,vcov=vcovHC(final_reg,type="HC1")))
```

### 10. Testing the new dataset
```{r new dataset test}
#testing results
#install.packages('caTools')
df_test <- read.csv("C:/YICHEN WANG/Course/2021 FALL/MGSC661/project/40_films_dataset_fall_2021.csv")
attach(df_test)
# dataframe only including predictors found from r-squared approach
df_test <- df_test[, c("imdb_score","budget_in_millions", "genre_drama", meaningful.predictors)] 

# dataframe also including predictors found from random forest
df_test$imdb_score = predict(fit2,df_test)
print(df_test$imdb_score)
write.csv(df_test,"C:/YICHEN WANG/Course/2021 FALL/MGSC661/project/40_films_dataset_fall_2021_result.csv", row.names = FALSE)

```